Simulation Learning in Computer Hex

### 2011-09-22 thesis/thesis.tex
Prettied up some pseudocode with the listings package.

\documentclass[11pt]{report}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\newcommand{\black}{\texttt{Black}}
\newcommand{\white}{\texttt{White}}
\newcommand{\blacks}{\texttt{Black's}}
\newcommand{\whites}{\texttt{White's}}
\newcommand{\loc}[1]{\texttt{#1}}
\begin{document}

@@

\section{Overview of the Thesis}\label{overview}
In Chapter \ref{mcts} we will review the current state of the art in Monte Carlo Tree Search (MCTS). MCTS is a technique to stochastically sample paths through a game-tree. It has been found to work well in games where: the tree is too large to consider brute-force search, no good solution exists to prune ``bad'' nodes, and no good evaluation function exists. Section \ref{bias} covers the current methods of biasing the tree search, including some methods similar to the technique presented in this paper. Chapter \ref{problem} covers why finding a generic way to bias the tree search would be a step forward in MCTS, with a formal definition of biasing the search, allowing a comparison of different but similar techniques. Chapter \ref{solution} presents a way of biasing the tree that can be automatically evolved through self-play, and does not require outside ``expert'' knowledge. Finally Chapter \ref{results} summarizes the technique and its usefulness, and discusses what can be done in the future to improve and extend it.

@@

\begin{verbatim}
function search(root):
  for i in range(simulations):
    step(root)

function play_from(node) returns outcome:
  if node.visits < threshold:
    outcome = simulate(node)
  else:
    child = select(node)
    outcome = play_from(child)
  if outcome is win for node's player:
    node.wins++
  node.visits++
  return outcome
\end{verbatim}
% TODO: figure with caption

>>>>

\documentclass[11pt]{report}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{url}
\newcommand{\black}{\texttt{Black}}
\newcommand{\white}{\texttt{White}}
\newcommand{\blacks}{\texttt{Black's}}
\newcommand{\whites}{\texttt{White's}}
\newcommand{\loc}[1]{\texttt{#1}}
\begin{document}

@@

\section{Overview of the Thesis}
In Chapter \ref{mcts} we will review the current state of the art in Monte Carlo Tree Search (MCTS). MCTS is a technique to stochastically sample paths through a game-tree. It has been found to work well in games where: the tree is too large to consider brute-force search, no good solution exists to prune ``bad'' nodes, and no good evaluation function exists. Section \ref{bias} covers the current methods of biasing the tree search, including some methods similar to the technique presented in this paper. Chapter \ref{problem} covers why finding a generic way to bias the tree search would be a step forward in MCTS, with a formal definition of biasing the search, allowing a comparison of different but similar techniques. Chapter \ref{solution} presents a way of biasing the tree that can be automatically evolved through self-play, and does not require outside ``expert'' knowledge. Finally Chapter \ref{results} summarizes the technique and its usefulness, and discusses what can be done in the future to improve and extend it.

@@

\begin{lstlisting}[float,frame=single,language=Python,caption=MCTS Algorithm Pseudocode]
def search(root):
  for i in range(simulations):
    step(root)

def play_from(node) returns outcome:
  if node.visits < threshold:
    outcome = simulate(node)
  else:
    child = select(node)
    outcome = play_from(child)
  if outcome is win for node.player:
    node.wins++
  node.visits++
  return outcome
\end{lstlisting}
